Done

### 2025-09-02 done.qmd
update

@@

2012-06-06: [Fundamentals of learning: the exploration-exploitation trade-off](done/2012-06-12.html)

2012-06-04: [New paper: A novel task for the investigation of action acquisition](done/2012-06-12.html)

>>>>

2020 - 2025 I was [Research Practice Lead](done/2025rpl.html) for the University of Sheffield

@@

2012-06-06: [Fundamentals of learning: the exploration-exploitation trade-off](done/2012-06-06.html)

2012-06-04: [New paper: A novel task for the investigation of action acquisition](done/2012-06-04.html)
